Disease and climate effects on individuals drive post-reintroduction

### 2018-11-17 article.Rmd
Minor typos

The two study lakes are located in eastern Yosemite National Park (California, USA) at elevations of 2880 and 3200 m. \textit{R. sierrae} populations in both lakes were established via translocation from a single nearby donor population (elevation: 3176 m). 
The donor population has been Bd-positive for at least two decades [@fellers2001oral], and contains one of the largest \textit{R. sierrae} populations in Yosemite (minimum population size during this study: 600-1500 adults). 
The introduction lakes are located 5.5-7.0 km from the donor population and both contain high quality \textit{R. sierrae} habitat (i.e., fishless, 6-12 m deep, with adjacent meadow and stream habitats) [@knapp2005effects]. 
Because these lakes harbor a sensitive species, we refer to them by the pseudonyms Alpine and Subalpine [@lindenmayer2017not]. 
At Alpine in the year 2001, five years prior to the translocation of adults into this lake, a single large adult R. sierrae was detected on a visual encounter survey [@knapp2005effects]. 
No \textit{R. sierrae} of any life stage was detected at Alpine on a visual encounter survey conducted three weeks prior to translocation in 2006. 
At Subalpine, a single \textit{R. sierrae} tadpole was observed on a visual encounter survey in 2001, seven years prior to adult translocations in 2008. 
Subsequent surveys in 2005 and 2007 did not detect \textit{R. sierrae} of any life stage at Subalpine.
Based on these observations and the widespread historical occurrence of \textit{R. sierrae} across similar lakes in Yosemite, we assumed that both lakes were historically occupied by \textit{R. sierrae}, and that these populations were extirpated prior to this study's translocations by the introduction of nonnative fish prior to 1977 and the arrival of Bd in the 1980s or 1990s based on historical declines of \textit{R. sierrae} observed at that time [@phillips1990have; @sherman1993population; @drost1996collapse].

@@

An imaginary first primary period augments the collection of primary periods when introductions took place and when surveys occurred, and was set to occur one week before the initial introductions into each population. 
For this augmented period $t = 1$, we assume that all individuals are in the ``not-recruited'' class, $u_{i, 1} = 1$ for $i = 1, ..., M$ (Figure 1). 
Given that neither lake was known to contain adult frogs immediately prior to introduction, this is potentially a fair assumption, but in case the assumption was violated and adults were present prior to the introduction, we include a time-varying adjustment into the recruitment model (described below).

@@

We thank the following people and institutions for important contributions to this study: numerous people who assisted with the field work (especially N. Kauffman, A. Killion, A. Lindauer, J. Maurer, and S. Ostoja); R. Chen, K. Rose, and M. Toothman for qPCR assistance; C. Briggs and M. Wilber for reviewing an earlier draft of the manuscript; and Yosemite National Park (R. Grasso, H. McKenny, and S. Thompson), U.S. Geological Survey - Western Ecological Research Center (M. Brooks and S. Ostoja), and  the University of California Natural Reserve System - Sierra Nevada Aquatic Research Laboratory (DOI: 10.21973/N3966F) for logistical support and valuable discussions. 
Research permits were provided by Yosemite National Park, U.S. Fish and Wildlife Service, and the Institutional Animal Care and Use Committee at the University of California, Santa Barbara. 
This project was funded by grants from the National Park Service (to R.A.K), Yosemite Conservancy (to Yosemite National Park and R.A.K.), U.S. Geological Survey (Ecosystems Mission Area - Natural Resource Preservation Program, to M. Brooks and R. Knapp for the project titled ``Factors influencing reintroduction success of the endangered mountain yellow-legged frog'', and National Science Foundation (DEB-1557190, to C. Briggs and R. Knapp).
We also thank H. Ito for translating mark-recapture model specifications from JAGS to Stan, as this greatly simplified our implementation.

>>>>

The two study lakes are located in eastern Yosemite National Park (California, USA) at elevations of 2880 and 3200 m. \textit{R. sierrae} populations in both lakes were established via translocation from a single nearby donor population (elevation: 3176 m). 
The donor population has been Bd positive for at least two decades [@fellers2001oral], and contains one of the largest \textit{R. sierrae} populations in Yosemite (minimum population size during this study: 600-1500 adults). 
The introduction lakes are located 5.5-7.0 km from the donor population and both contain high quality \textit{R. sierrae} habitat (i.e., fishless, 6-12 m deep, with adjacent meadow and stream habitats) [@knapp2005effects]. 
Because these lakes harbor a sensitive species, we refer to them by the pseudonyms Alpine and Subalpine [@lindenmayer2017not]. 
At Alpine in the year 2001, five years prior to the translocation of adults into this lake, a single large adult R. sierrae was detected on a visual encounter survey [@knapp2005effects]. 
No \textit{R. sierrae} of any life stage was detected at Alpine on a visual encounter survey conducted three weeks prior to translocation in 2006. 
At Subalpine, a single \textit{R. sierrae} tadpole was observed on a visual encounter survey in 2001, seven years prior to adult translocations in 2008. 
Subsequent surveys in 2005 and 2007 did not detect \textit{R. sierrae} of any life stage at Subalpine.
Based on these observations and the widespread historical occurrence of \textit{R. sierrae} across similar lakes in Yosemite, we assumed that both lakes were historically occupied by \textit{R. sierrae}, and that these populations were extirpated prior to this study's translocations by the introduction of nonnative fish prior to 1977 and the arrival of Bd in the 1980s or 1990s based on historical declines of \textit{R. sierrae} observed at that time [@phillips1990have; @sherman1993population; @drost1996collapse].

@@

An imaginary first primary period augments the collection of primary periods when introductions took place and when surveys occurred, and was set to occur one week before the initial introductions into each population. 
For this augmented period $t = 1$, we assume that all individuals are in the ``not-recruited'' class, $u_{i, 1} = 1$ for $i = 1, ..., M$ (Figure 1). 
Given that neither lake was known to contain adult frogs immediately prior to introduction, this is potentially a fair assumption, but in case the assumption was violated and adults were present prior to the introduction, we include a time-varying adjustment into the recruitment model (see Parameter model - 2. Recruitment model).

@@

We thank the following people and institutions for important contributions to this study: numerous people who assisted with the field work (especially N. Kauffman, A. Killion, A. Lindauer, J. Maurer, and S. Ostoja); R. Chen, K. Rose, and M. Toothman for qPCR assistance; C. Briggs and M. Wilber for reviewing an earlier draft of the manuscript; and Yosemite National Park (R. Grasso, H. McKenny, and S. Thompson), U.S. Geological Survey - Western Ecological Research Center (M. Brooks and S. Ostoja), and  the University of California Natural Reserve System - Sierra Nevada Aquatic Research Laboratory (DOI: 10.21973/N3966F) for logistical support and valuable discussions. 
Research permits were provided by Yosemite National Park, U.S. Fish and Wildlife Service, and the Institutional Animal Care and Use Committee at the University of California, Santa Barbara. 
This project was funded by grants from the National Park Service (to R.A.K), Yosemite Conservancy (to Yosemite National Park and R.A.K.), U.S. Geological Survey (Ecosystems Mission Area - Natural Resource Preservation Program, to M. Brooks and R. Knapp for the project titled ``Factors influencing reintroduction success of the endangered mountain yellow-legged frog''), and National Science Foundation (DEB-1557190, to C. Briggs and R. Knapp).
We also thank H. Ito for translating mark-recapture model specifications from JAGS to Stan, as this greatly simplified our implementation.
